%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Engineering Manager} % Job title
    {Enhesa (Boost IT)} % Organization
    {Lisbon, Portugal} % Location
    {Jan. 2025 - Present} % Date(s)
    {
      \item Within a team of 3 Engineering Managers, responsible for leading the engineering team, ensuring that the team is aligned with the company's goals and objectives.
      \item Coordination of two teams of 5 people each responsible for the migration of an old monolithical application to a microservices architecture.
    }

%---------------------------------------------------------
  \cventry
    {Tech Lead \> Principal Engineer \> Solution Architect} % Job title
    {Carlsberg GBS (Boost IT)} % Organization
    {Lisbon, Portugal} % Location
    {Jan. 2019 - Dec. 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Started as Tech Lead in a sales forces internal tool, leading a team of 4 people who grew to 18. Green fielded, the tool is platform and device-agnostic, allowing Carlsberg's sales representatives to have access to customer data in the field.
        \item Moved then to a Principal Engineer role, within a team of 5.
        Responsible to drive the innovation, solution design and architecture of Carlsberg's digital products; discuss requirements with the business team; mentor the technical teams and give hands-on support; design and develop proof of concepts.
        \item In the last two years, worked as a Solution Architect.
        Responsible for communicating with stakeholders, gathering business requirements and designing the architecture of the solution, ensuring that best practices and guidelines are being respected, analyzing infrastructure requirements leveraging AWS cloud services and coordinating several teams and disciplines to achieve the best solution for every request.
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Developer} % Job title
    {Prime IT Nearshore} % Organization
    {Lisbon, Portugal} % Location
    {Apr. 2018 - Jan. 2019} % Date(s)
    {
    }

%---------------------------------------------------------
  \cventry
    {Senior Developer \& Team Lead} % Job title
    {Stef IT (Novabase)} % Organization
    {Lisbon, Portugal} % Location
    {Apr. 2016 - Apr. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Main developer and team lead of a project in the logistics area.
        \item Responsible for bridging the gap between the business located in France and the technical team, in Lisbon, gathering requirements and translating them into technical solutions.
        \item Development and maintenance of several technical solutions based on an event-driven SOA architecture.
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Developer} % Job title
    {Bouygues Telecom (Altran)} % Organization
    {Lisbon, Portugal} % Location
    {Nov. 2015 - Apr. 2016} % Date(s)
    {
    }

%---------------------------------------------------------
  \cventry
    {Developer \> Senior Developer \> Team Leader} % Job title
    {BNP Paribas Securities Services} % Organization
    {Lisbon, Portugal} % Location
    {Jul. 2009 - Jul. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Green fielding of a new project for cash investigation tickets management.
        \item Requirements gathering and communication with the business team located in Paris, France.
        \item Team leading of a team of 4 people in the last two years, being responsible for daily activities and tasks management.
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Developer \> Team Leader} % Job title
    {Janela Digital} % Organization
    {Caldas da Rainha, Portugal} % Location
    {Jul. 2007 - Jul. 2009} % Date(s)
    {
    }

%---------------------------------------------------------
  \cventry
    {Developer} % Job title
    {Nokia Siemens Networks} % Organization
    {Lisbon, Portugal} % Location
    {Jun. 2006 - Jun. 2007} % Date(s)
    {
    }

%---------------------------------------------------------
  \cventry
    {Junior Developer} % Job title
    {Portugal Telecom Sistemas de Informação} % Organization
    {Lisbon, Portugal} % Location
    {Jul. 2004 - Jul. 2006} % Date(s)
    {
    }

%---------------------------------------------------------
\end{cventries}
